Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-07-24 paper-correlations.tex
Add missing citation

Before computation of chord length function an input array must be pre-processed
to find an interface for the phase of interest. For this purpose we use
distance transform function defined as follows:
\begin{equation}
  \mathcal{D}(\bm{x})= \left\{
  \begin{array}{ll}
    0 & \quad \bm{x} \in \text{solid phase} \\
    \min\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
  \end{array}
\right. \label{eq:distance-transform}
\end{equation}
For distance transform has many implementations \textcolor{red}{cite
  something}. In \code{chord\_length} function we firstly apply distance
transform to an input to find the interface and then accumulate chord length in
per-slice manner. Finally, chord lengths can be binned in a histogram.
\begin{algorithmic}[1]
  \Procedure{chord\_length}{$A, phase$}
    \State $A' \gets I^{(phase)}(A)$
    \State $A_E \gets \mathcal{D}(A') = 1$
    \Comment We consider elements for which the distance transform equals to $1$
    to be part of the interface
    \State $chord\_list \gets [\ ]$
    \ForAll{$(S', S_E) \in zip(slices(A'), slices(A_E))$}
      \Comment iterate through all one-dimensional slices in $A'$ and
      corresponding slices in $A_E$
      \State $l \gets 0$
      \State $maybe\_chord \gets False$
      \For{$idx \gets 0, length(S')-1$}
        \If{$S_E[idx]$}
          \Comment Interface found
          \If{$l > 1\ and\ maybe\_chord$}
            \Comment Chord found
            \State $chord\_list \gets l:chord\_list$
          \EndIf
          \State $l \gets 0$
          \State $maybe\_chord \gets True$
        \ElsIf{$\neg S'[idx]$}
          \Comment We are not in the phase of interest
          \State $maybe\_chord \gets False$
        \EndIf
      \EndFor
    \EndFor
    \State \textbf{return} $chord\_list$ or $histogram(chord\_list)$
  \EndProcedure
\end{algorithmic}
This implementation also works in linear time.

>>>>

Before computation of chord length function an input array must be pre-processed
to find an interface for the phase of interest. For this purpose we use
distance transform function defined as follows:
\begin{equation}
  \mathcal{D}(\bm{x})= \left\{
  \begin{array}{ll}
    0 & \quad \bm{x} \in \text{solid phase} \\
    \min\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
  \end{array}
\right. \label{eq:distance-transform}
\end{equation}
There are many algorithms for distance transform, including algorithms performed
in linear time \cite{DT}.In \code{chord\_length} function we firstly apply
distance transform to an input to find the interface and then accumulate chord
length in per-slice manner. Finally, chord lengths can be binned in a histogram.
\begin{algorithmic}[1]
  \Procedure{chord\_length}{$A, phase$}
    \State $A' \gets I^{(phase)}(A)$
    \State $A_E \gets \mathcal{D}(A') = 1$
    \Comment We consider elements for which the distance transform equals to $1$
    to be part of the interface
    \State $chord\_list \gets [\ ]$
    \ForAll{$(S', S_E) \in zip(slices(A'), slices(A_E))$}
      \Comment iterate through all one-dimensional slices in $A'$ and
      corresponding slices in $A_E$
      \State $l \gets 0$
      \State $maybe\_chord \gets False$
      \For{$idx \gets 0, length(S')-1$}
        \If{$S_E[idx]$}
          \Comment Interface found
          \If{$l > 1\ and\ maybe\_chord$}
            \Comment Chord found
            \State $chord\_list \gets l:chord\_list$
          \EndIf
          \State $l \gets 0$
          \State $maybe\_chord \gets True$
        \ElsIf{$\neg S'[idx]$}
          \Comment We are not in the phase of interest
          \State $maybe\_chord \gets False$
        \EndIf
      \EndFor
    \EndFor
    \State \textbf{return} $chord\_list$ or $histogram(chord\_list)$
  \EndProcedure
\end{algorithmic}
This implementation also works in linear time.
